\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{needspace}
\usepackage{setspace}

% ---------- PAGE SETUP ----------
\geometry{
 a4paper,
 total={170mm,257mm},
 left=22mm,
 top=22mm,
}

\setstretch{1.1}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\pagestyle{empty}

% ---------- CUSTOM COMMANDS ----------
\newcommand{\myName}[1]{\Huge \textbf{#1}}

\newcommand{\myContact}[1]{\small #1}

\newcommand{\sectionTitle}[1]{
    \par\vspace{12pt}
    \Needspace{3\baselineskip}
    \noindent\textbf{\large #1}
    \par\vspace{2pt}\hrule\vspace{6pt}
}

\newcommand{\resumeEntry}[4]{
    \begin{itemize}[leftmargin=*, label={}]
        \item \textbf{#1} \hfill #2
        \item \textit{#3} \hfill #4
    \end{itemize}
}

\newcommand{\projectEntry}[2]{
    \begin{itemize}[leftmargin=*, label={}]
        \item \textbf{#1} \hfill \href{#2}{\small{[Live Link]}}
    \end{itemize}
}

\newcommand{\descriptionItem}[1]{
    \begin{itemize}[leftmargin=2em, itemsep=4pt, topsep=4pt]
        \item #1
    \end{itemize}
}

\newcommand{\skillList}[2]{
    \begin{itemize}[leftmargin=*, label={}]
        \item \textbf{#1:} #2
    \end{itemize}
}

\newcommand{\certificationEntry}[2]{
     \begin{itemize}[leftmargin=*, label={}]
        \item #1 \hfill \textit{#2}
     \end{itemize}
}

% ---------- DOCUMENT START ----------
\begin{document}

% ----- HEADER -----
\begin{center}
    \myName{Premkumar Lande} \\[4pt]
    \myContact{
    Pune, Maharashtra |
    +91-9309954419 |
    \href{mailto:premkumarlande.skn.comp@gmail.com}{premkumarlande.skn.comp@gmail.com} |
    \href{https://premkumar324.github.io/projects/index.html}{Portfolio}
    }
\end{center}

% ----- SUMMARY -----
\sectionTitle{Summary}

Placement-ready final-year Computer Science student with strong foundations in Data Structures and Algorithms, Object-Oriented Programming, and Database Management Systems. Experienced in full-stack web development using React.js, Node.js, Express.js, MongoDB, and Appwrite. Currently working as a MERN Stack Intern and seeking Software Engineer opportunities.

% ----- EXPERIENCE -----
\sectionTitle{Experience}

\resumeEntry
{MERN Stack Intern}
{05/2026 -- Present}
{Wargstech, Pune}
{Performance-Based Internship}

\descriptionItem{Developing and maintaining full-stack web applications using MongoDB, Express.js, React.js, and Node.js.}

\descriptionItem{Building responsive user interfaces and backend APIs for business and educational platforms.}

\descriptionItem{Collaborating with developers and stakeholders to implement new features and improve existing workflows.}

\descriptionItem{Using Git and GitHub for version control, code management, and team collaboration.}

\descriptionItem{Participating in debugging, testing, deployment, and performance optimization activities.}

% ----- EDUCATION -----
\sectionTitle{Education}

\resumeEntry
{B.E. - Computer Science \& Engineering}
{08/2022 -- 07/2026}
{Shrimati Kashibai Navale College Of Engineering, Pune}
{CGPA: 8.26/10}

\resumeEntry
{CBSE 12th}
{2022}
{Army Public School, Pune}
{Percentage: 74.60\%}

\resumeEntry
{CBSE 10th}
{2020}
{Army Public School, Pune}
{Percentage: 88.88\%}

% ----- SKILLS -----
\sectionTitle{Skills}

\skillList{Languages}{JavaScript, Java, C++, SQL}

\skillList{Frontend}{React.js, Redux Toolkit, Tailwind CSS, HTML/CSS}

\skillList{Backend}{Node.js, Express.js, REST APIs, Appwrite}

\skillList{Databases \& AI}{MongoDB, SQL, RAG, Vector Search, AI Integration}

\skillList{Developer Tools}{Git, GitHub, Vercel, Postman, JWT Auth}

\skillList{CS Fundamentals}{Data Structures and Algorithms (DSA), Object-Oriented Programming (OOPs), Database Management Systems (DBMS)}

% ----- PROJECTS -----
\sectionTitle{Projects}

\projectEntry
{SinhgadConnect -- AI-Powered College Community Platform}
{https://premkumar324.github.io/projects/index.html}

\descriptionItem{Engineered a full-stack community platform enabling students to share posts, questions, and announcements using React.js, Node.js, Express.js, and MongoDB.}

\descriptionItem{Implemented a Retrieval Augmented Generation (RAG) chatbot that retrieves relevant posts via cosine similarity and generates grounded responses using Google Gemini API.}

\descriptionItem{Built semantic search using 768-dimensional embeddings for intelligent content discovery.}

\descriptionItem{Integrated AI-powered features including automatic post summarization, sentiment analysis, and tag generation.}

\descriptionItem{Designed a responsive React frontend with real-time updates and a modern user experience.}

\projectEntry
{Pixie -- Photo Sharing Social App}
{https://pixie-photo-sharing-app.vercel.app/}

\descriptionItem{Designed, developed, and deployed a full-stack social media application enabling real-time photo uploads and a dynamic public feed using React.js and Appwrite.}

\descriptionItem{Implemented secure authentication and profile management features to ensure user data privacy.}

\descriptionItem{Built responsive user interfaces and optimized performance for seamless user experience across devices.}

\descriptionItem{Leveraged Appwrite's Backend-as-a-Service capabilities for database management, authentication, and storage.}

% ----- CERTIFICATIONS -----
\sectionTitle{Certifications}

\certificationEntry
{Data Structures and Algorithms with C++}
{Physics Wallah | 03/2024}

\certificationEntry
{SQL and Relational Database 101}
{IBM | 07/2025}

\certificationEntry
{Java Complete Java Core}
{Udemy | 08/2025}

\end{document}
